%-------------------------
% Resume in Latex
% Author : Jorge Saravia
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Jorge Saravia} \\ \vspace{8pt}
    \href{tel:+xxxxxxxx}{\underline{\faicon{phone} \small +(xxx) xxxx-xxxx}} $|$ 
    \href{mailto:j@gmail.com}{\underline{\faicon{envelope} j@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jorge-saravia/}{\underline{ \faicon{linkedin} linkedin.com/in/jorge-saravia}}
\end{center}
\begin{center}
  \href{https://github.com/jsaravia36}{\underline{ \faicon{github} github.com/jsaravia36}} $ (current job)|$
  \href{https://github.com/shadowblaze36}{\underline{\faicon{github} github.com/shadowblaze36}} $(personal)$
  
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Privada de San Pedro (USAP)}{San Pedro Sula, Honduras}
      {Bachelor of Arts in Computer Science, Minor in Networking}{Aug. 2017 -- Sep. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
  {Fullstack Developer}{Nov. 2022 -- Present}
  {Zonamerica}{Montevideo, Uruguay}
  \resumeItemListStart
    \resumeItem{Worked on a React Native project to develop a cross-platform mobile app for a large retail client.}
    \resumeItem{Developed and maintained RESTful APIs using .NET Web API, and integrated with external systems using JSON and XML}
    \resumeItem{Troubleshoot and resolve technical issues, including bugs, performance bottlenecks, and production incidents.}
    \resumeItem{Collaborate with cross-functional teams, including product managers, designers, and other developers, to define product features and requirements.}
  \resumeItemListEnd

  \resumeSubheading
    {Software Developer}{Jan. 2022 -- Nov. 2022}
    {Tegra}{San Pedro Sula, Honduras}
    \resumeItemListStart
      \resumeItem{Built Enterprise level tools for industrial processes.}
      \resumeItem{Implemented CI/CD on all ongoing projects.}
      \resumeItem{Developed and maintained multiple mobile apps for the manufacturing area.}
      \resumeItem{Gathered and reorganized all internal developments in Azure DevOps.}
      \resumeItem{Worked together with other companies, such as Nike and Fanatics.}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

\resumeSubheading
{Web Developer}{Feb. 2020 -- Dec. 2021}
{Credisol}{San Pedro Sula, Honduras}
\resumeItemListStart
  \resumeItem{Cooperated with designers to create clean interfaces and simple, intuitive interactions and experiences.}
  \resumeItem{Worked with senior developers to manage large, complex design projects for corporate clients.}
  \resumeItem{Completed detailed programming and development tasks for front-end public and internal websites as well as challenging back-end server code.}
  \resumeItem{Used Java and JSF to build a banking platform for a financial services client, implementing payment integrations and order tracking features.}
  \resumeItem{Carried out quality assurance tests to discover errors and optimize usability.}
  \resumeItem{Obtained various trainings focused on the financial area.}
\resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Certificates}

  % \resumeSubHeadingListStart
  %   \resumeSubheading
  %     {Udemy}{Dec. 2021 -- May 2022}
  %     {Flutter: Your complete development guide for iOS and Android }{ude.my/UC-0be83af6-6c2c-459d-841f-9fbfbb6c3570}
  % \resumeSubHeadingListEnd

  % \resumeSubHeadingListStart
  %   \resumeSubheading
  %     {Google Activate}{Jan. 2020 -- Mar. 2020}
  %     {E-commerce }{ID: TSW XJ2 89R}
  % \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
  \resumeSubheading
    {C\# Fundamentals}{Pluralsight}
    {id: 0096b00d-2398-435a-82f7-3f5401408ab1}{Nov. 2022}
\resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {Clean Coding Principles in C\# }{Pluralsight}
      {id: f603b478-ee6d-4cd2-b509-5aa8e2005abc}{Sep. 2022}
  \resumeSubHeadingListEnd

  

  \resumeSubHeadingListStart
    \resumeSubheading
      {Flutter: Your complete development guide for iOS and Android }{Udemy}
      {ude.my/UC-0be83af6-6c2c-459d-841f-9fbfbb6c3570}{May 2022}
  \resumeSubHeadingListEnd

  \resumeSubHeadingListStart
    \resumeSubheading
      {E-commerce}{Google Activate}
      {id: TSW XJ2 89R}{Mar. 2020}
  \resumeSubHeadingListEnd


%

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C\#, Dart, JavaScript, SQL, HTML/CSS} \\
     \textbf{Frameworks}{: ReactJs, React Native, Xamarin, Flutter, .Net, Android Studio, Spring, JSF} \\
     \textbf{Developer Tools}{: Git, Docker, Xcode, VS Code, Visual Studio, Rider, IntelliJ, Postman, Azure Data Studio, SQL Managment Studio} \\
     \textbf{Other Skills}{: SVN, Jira, Scrum, Finance, Azure Devops, CI/CD, Project Managment, Restful Apis}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}